\subsection{The Zombie Strategy}
The zombies are dumb but they see the survivor.
The survivor's only hope is to flee forever using infinite stamina.

If a graph is connected, then there must exist some path connecting $z$, $s$.
Indeed, there must be a shortest such path.
But there can also be arbitrarily many shortest paths connecting two vertices.

[insert lattice type graph with many paths between two vertices]

Consider the set of all possible paths between the zombie and the survivor.
We are primarily interested in the shortest possible paths since these
paths dictate the zombie strategy at the beginning of each round. We sometimes
refer to as $zs$-paths or ``zombie-survivor paths''.

Note that if there are multiple $zs$-paths for a given round then they must all have
the same length. Otherwise something doesn't add up.


\subsection{Keep Your Distance}

\begin{lemma}

  Consider an arbitrary zombie $z_r$ at round $r$.
  Then
  \[d(z_r, s_r) \leq \text{diam}(G) \]
  Moreover, for all $r \geq 1$ the sequence $d(z_r, s_r)$ of distances is non-inceasing, i.e.,
  \[ d(z_{r+1}, s_{r+1}) \leq d(z_r, s_r)\]
\end{lemma}

\begin{proof}
The first part follows from the definition of the diameter of the graph.

If $z_i = s_i$, then $d(z_i, s_i) = 0$ and the game is over. We may consider the
game to be finished (and the sequence thus finite and non-increasing)
or suppose that the zombie mirrors the survivor forever and thereby obtain a sequence
of zeroes (which is non-increasing).

Otherwise, we have $z_i \not= s_i$ and, since $G$ is connected, there exists a shortest $z_is_i$-path. Say

EDIT: reverse order so that $u_1$ is next move?

\[ P : z_i = u_0, u_1, \dots, u_k = s_i \]

so that $d(z_i, s_i) = k$.

On round $i+1$, the zombie must move to $z_{i+1} \in N(z_i)$ such that $d(z_{i+1}, s_i) < d(z_i, s_i)$.
In fact, in the graph distance model we have precisely $d(z_{i+1}, s_i) = d(z_i, s_i) - 1$.
We can suppose that $z_{i+1} = u_1$ is the next vertex along $P$.

In response, the survivor moves to $s_{i+1} \in N[s_i]$. Then

\[ P' : z_{i+1} = u_1, u_2, \dots, u_k, s_{i+1} \]

is a $z_{i+1}s_{i+1}$-path of length at most $k$. So the length of a shortest zombie-survivor
path on round $i+1$ is at most $k = d_i$. So $d_{i+1} \leq d_i$.
\end{proof}


EDIT: Remove next part? Useless.
We can consider these distance sequences to be infinite.
\begin{corollary} A zombie-win distance sequence has finite support.
A survivor-win distance sequence must be eventually constant and $d_k > 1$
for every round $k \geq 1$.
\end{corollary}

\subsection{There is No Hope}
Which are the graphs for which a single zombie is guaranteed to capture the
survivor?

It is pretty clear that the survivor has little chance if the graph is a
a simple path $P_n$.

[insert graph of long path here haha]

Indeed, any finite acyclic graph is zombie win since an acyclic and connected graph
has a unique path connecting any $z, s \in V(T)$. Every step the zombie takes towards
the survivor limits the survivor's movement. And options.

Maximally outer-planar graph.
